First and foremost, thank you to my advisor Prof. Daniel Nosenchuck for lending me your guidance both throughout this project and for the last four years. From being my freshman year advisor to thesis advisor, we have been through a lot together and you helped me realize what I am truly capable of. Thank you on taking me on when no one else would, even when you were fully booked.

A big thank you to my second advisor Alexander Gaillard. From doing Zoom labs on a laptop in a cart to working on a real-life video game prop to now a face tracking robot, you have helped me grow immeasurably as an engineer at Princeton and I will be forever thankful for having you as a mentor and as a friend.

I'd also like to thank Glenn Northey for helping me around the machine shop with random questions and giving me the resources and the space to succeed.

Thank you to Jonathan Prevost for helping me out with the microelectronics. The project would have gone up in flames without your help.

I would also like to thank SEAS for the generous funding that made this project possible. I would have never been able to afford this kind of project on my own, so I am truly grateful for the opportunity given to me.

Thank you to my friends at Princeton, from the uncountable amount of hours eating meals together at Colo to getting up to late night shenanigans, it's been a wild ride. There were many ups and downs along these four years, but you guys made it all worth it in the end and will always hold a special place in my heart.

And lastly thank you to all the people who provide information on the Internet publicly and for free. This project would not have been possible without the help of countless posts on websites like Arduino forums, Stack Overflow, and YouTube. The internet today is a vast collection of knowledge in almost any subject you can dream of. The resources that are available to me today are incredible compared to just a couple years ago, and I try not to take it for granted. I hope that one day I will be able to return the favor.